### 2023-03-24 README.Rmd
Update readme.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TICA: Dimensions of land transitions impacts in the Cerrado and Amazon <a href="https://hugotseixas.com/en/tica/"><img src="man/figures/logo.png" align="right" height="138" /></a>

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "/man/figures/README-",
  out.width = "100%"
)
```

# TICA: Dimensions of land transitions impacts in the Cerrado and Amazon <a href="https://hugotseixas.com/en/tica/"><img src="/man/figures/logo.png" align="right" height="138" /></a>
